---
title:"paleoscape data/plots"
date: "Apil 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
library(RCurl)
knitr::opts_chunk$set(echo = TRUE)
```

#Experiment 1
 
Experiment setup:
  1 repetition, 240 time limit

Variables:
  ["walk-speed" 2]
  ["map-zone" "full"]
  ["nragents" 30]
  ["max_kcal_to_harvest" 3000]
  ["days_of_foresight" 1]
  ["plots?" false]
  ["vision-camp" 50]
  ["display-mode" "time-replenished"]
  ["global-knowledge?" true]
  ["discount_rate" 0.1]
  ["daily-time-budget" 5.9]
  ["nrcamps" 20]
  ["spatial-foresight" true]
  ["vision-forager" 10]
  ["camp-move-threshold" 1500]
  ["hunter-percent" 0.5]
  ["forager-movement" "local-patch-choice"]

Reporters: 
  kcal-avg
  sum [times-harvested * kcal_return] of patches with [vt = 1]
  sum [times-harvested * kcal_return] of patches with [vt = 2]
  sum [times-harvested * kcal_return] of patches with [vt = 3]
  sum [times-harvested * kcal_return] of patches with [vt = 4]
  sum [times-harvested * kcal_return] of patches with [vt = 5]
  sum [times-harvested * kcal_return] of patches with [vt = 6]
  sum [times-harvested * kcal_return] of patches with [vt = 7]
  sum [times-harvested * kcal_return] of patches with [vt = 8]
  sum [times-harvested * kcal_return] of patches with [vt = 9]
  sum [times-harvested * kcal_return] of patches with [vt = 10]
  sum [times-harvested * kcal_return] of patches with [vt = 11]
  sum [times-harvested * kcal_return] of patches with [vt >= 12]
  mean [days_without] of camps / ticks
  mean [days_without] of agents / ticks
  timer
  mean [distance min-one-of patches with [goodcoast? = true] [distance myself]] of camps

Commands:
  Measure uns at evey step
  Setup: 
    reset-timer
    setup
  Go: 
    repeat 15 [go]
  
##read data

```{r}
require(ggplot2)
E1<-read.csv("Paleoscape_v4.2_experiment3-table.csv", header = TRUE,skip = 6,comment.char ="#")

names(E1)[c(1, 19:36)] <- c("run_number", "step", "kcal_avg", "Freshwater_wetlands", "Alluvial_Vegetation", "Strandveld", "Saline_Vegetation", "Renosterveld", "Sand_Fynbos", "v7", "Thicket", "Limestone_Fynbos", "Aeolianite_Coastal", "Sandy_Beach_Coastal", "TMS_Boulders_Coastal", "avg-days-no-camps","avg-days-no-agents", "timer","distance-from-coast")

#read a source code for a function that plots multiple ggplots in one layer

source("multiplot_function.R")
```

# Plot 1: avg kcal

```{r, fig.width=18,fig.height=8}
P1=ggplot(subset(E1, nragents == 30), aes(x = step, y = kcal_avg)) +
  geom_line()+
   labs(x = "tick = 15 days", y="average kcal")+
theme(text = element_text(size=18))
P2=ggplot(subset(E1, nragents == 30), aes(x = step, y = kcal_avg)) +
  geom_point()+
   labs(x = "days", y="average kcal")+
theme(text = element_text(size=18))+
    geom_smooth(span=1,method = "lm")

multiplot(P1, P2, cols=2)
```

